---
title: "Auto Z-Curve Report"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    smooth-scroll: true
    embed-resources: true
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(dplyr)
library(jsonlite)
library(knitr)
library(readr)
library(zcurve)

project_dir <- Sys.getenv("AUTO_ZCURVE_PROJECT_DIR")
output_dir <- Sys.getenv("AUTO_ZCURVE_OUTPUT_DIR", file.path(project_dir, "output"))
repo_dir <- Sys.getenv("AUTO_ZCURVE_REPO_DIR")
schema_path <- Sys.getenv("AUTO_ZCURVE_SCHEMA_PATH", file.path(project_dir, "extraction_schema.yml"))
instruction_path <- Sys.getenv("AUTO_ZCURVE_INSTRUCTIONS_PATH", file.path(repo_dir, "config", "statistic_extraction_instructions.md"))
model_name <- Sys.getenv("AUTO_ZCURVE_MODEL_NAME")
effect_definition <- Sys.getenv("AUTO_ZCURVE_EFFECT_DEFINITION")

source(file.path(repo_dir, "R", "utils.R"))
source(file.path(repo_dir, "R", "schema.R"))
source(file.path(repo_dir, "R", "report.R"))

config <- read_extraction_config(schema_path)
results_path <- file.path(output_dir, "extractions.json")
run_log_path <- file.path(output_dir, "run_log.json")

results <- if (file.exists(results_path)) {
  jsonlite::read_json(results_path, simplifyVector = FALSE)
} else {
  list()
}

run_log_raw <- if (file.exists(run_log_path)) {
  jsonlite::read_json(run_log_path, simplifyVector = TRUE)
} else {
  data.frame()
}

run_log <- tibble::as_tibble(run_log_raw)
effect_table <- flatten_results(results, config)
zcurve_bundle <- run_zcurve_analysis(effect_table, config)
disclosure_table <- zcurve_bundle$disclosure_table %||% effect_table

if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

readr::write_csv(disclosure_table, file.path(output_dir, "disclosure_table.csv"))

zcurve_summary_text <- if (!identical(zcurve_bundle$status, "ok")) {
  message <- zcurve_bundle$message
  if (is.null(message) || !nzchar(message)) {
    "Z-curve could not be estimated."
  } else {
    as.character(message)
  }
} else {
  paste(capture.output(summary(zcurve_bundle$fit, all = TRUE)), collapse = "\n")
}
writeLines(zcurve_summary_text, file.path(output_dir, "zcurve_summary.txt"), useBytes = TRUE)

generated_at <- format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z")
instructions_text <- build_system_prompt(config, instruction_path, effect_definition)

truncate_report_text <- function(x, max_chars = 180) {
  if (is.null(x)) {
    return(NA_character_)
  }

  x <- as.character(x)
  x <- gsub("\\s+", " ", x)
  too_long <- !is.na(x) & nchar(x) > max_chars
  x[too_long] <- paste0(substr(x[too_long], 1, max_chars - 1), "…")
  x
}

successful_pdfs <- sum(vapply(results, function(item) identical(item$status, "ok"), logical(1)))
failed_pdfs <- sum(vapply(results, function(item) !identical(item$status, "ok"), logical(1)))
total_pdfs <- successful_pdfs + failed_pdfs
extracted_effects <- nrow(effect_table)
sum_result_number <- function(field) {
  values <- vapply(results, function(item) {
    value <- item[[field]]
    if (is.null(value) || length(value) == 0 || is.na(value)) {
      return(0)
    }
    as.numeric(value)
  }, numeric(1))
  sum(values, na.rm = TRUE)
}
input_tokens <- sum_result_number("input_tokens")
output_tokens <- sum_result_number("output_tokens")
total_tokens <- sum_result_number("total_tokens")
usable_inputs <- if (nrow(disclosure_table) && "usable_for_zcurve" %in% names(disclosure_table)) {
  sum(disclosure_table$usable_for_zcurve %in% TRUE, na.rm = TRUE)
} else {
  0
}
articles_with_effects <- if (nrow(effect_table) && "source_name" %in% names(effect_table)) {
  dplyr::n_distinct(effect_table$source_name)
} else {
  0
}
failed_results <- purrr::keep(results, function(item) !identical(item$status, "ok"))
disclosure_csv_path <- file.path(output_dir, "disclosure_table.csv")

rel_to_project <- function(path) {
  proj <- normalizePath(project_dir, mustWork = FALSE)
  p    <- normalizePath(path, mustWork = FALSE)
  if (startsWith(p, paste0(proj, "/"))) substring(p, nchar(proj) + 2L) else path
}
```

<style>
body {
  line-height: 1.45;
}

.quarto-title-block .title {
  margin-bottom: 0.25rem;
}

.setup-list {
  margin: 0 0 1rem;
  padding-left: 1.1rem;
}

.setup-list li {
  margin: 0.25rem 0;
}

details {
  border: 1px solid #d7dde8;
  border-radius: 8px;
  padding: 0.75rem 1rem;
  margin: 1rem 0;
  background: #fbfcfe;
}

summary {
  cursor: pointer;
  font-weight: 650;
}

pre {
  white-space: pre-wrap;
  word-break: break-word;
  overflow-x: auto;
}
</style>

## Overview

This report was generated from `r total_pdfs` PDF article`r if (total_pdfs == 1) "" else "s"`.
Extraction succeeded for `r successful_pdfs` article`r if (successful_pdfs == 1) "" else "s"` and failed for `r failed_pdfs`.

The successful extractions produced `r extracted_effects` effect`r if (extracted_effects == 1) "" else "s"` from `r articles_with_effects` article`r if (articles_with_effects == 1) "" else "s"`.
Of those effects, `r usable_inputs` had statistics usable as z-curve inputs.

Gemini usage recorded `r input_tokens` input tokens and `r output_tokens` output tokens (`r total_tokens` total).

The full disclosure table is available as a separate CSV at:

```{r results='asis'}
cat("`", rel_to_project(disclosure_csv_path), "`", sep = "")
```

## Z-Curve

### Full Output

The complete z-curve summary is shown below.

```{r results='asis'}
bundle <- zcurve_bundle

if (!identical(bundle$status, "ok")) {
  cat(if (is.null(bundle$message) || !nzchar(bundle$message)) "Z-curve could not be estimated." else bundle$message)
} else {
  cat("```text\n")
  cat(zcurve_summary_text)
  cat("\n```\n")
}
```

### Metrics

```{r}
bundle <- zcurve_bundle

if (!identical(bundle$status, "ok")) {
  cat(if (is.null(bundle$message) || !nzchar(bundle$message)) "Z-curve could not be estimated." else bundle$message)
} else {
  kable(bundle$metrics)
}
```

### Plot

```{r fig.width=10, fig.height=7}
bundle <- zcurve_bundle

if (identical(bundle$status, "ok")) {
  plot(bundle$fit, annotation = TRUE, CI = TRUE)
}
```

## Disclosure Table

The disclosure table is not embedded in this HTML report to keep the report readable.
Use the separate CSV file for inspection, filtering, and audit work: `r rel_to_project(disclosure_csv_path)`.

## Batch Summary

### Failed Articles

```{r results='asis'}
if (length(failed_results)) {
  for (item in failed_results) {
    source_name <- item$source_name %||% item$file_name %||% item$source_file %||% "Unknown source"
    reason <- item$error %||% "No failure reason was recorded."
    reason <- truncate_report_text(reason, max_chars = 500)
    cat("- **", source_name, "**: ", reason, "\n", sep = "")
  }
} else {
  cat("No articles failed during extraction.")
}
```

## Setup

<ul class="setup-list">
  <li><strong>Generated:</strong> `r generated_at`</li>
  <li><strong>Gemini model:</strong> `r model_name`</li>
  <li><strong>Schema:</strong> `r config$name`</li>
  <li><strong>Schema file:</strong> `r rel_to_project(schema_path)`</li>
  <li><strong>Instruction file:</strong> `r rel_to_project(instruction_path)`</li>
</ul>

<details>
<summary>Configured extraction instructions</summary>

```{r results='asis'}
cat("```text\n")
cat(instructions_text)
cat("\n```\n")
```

</details>
