---
title: "Reproduce the Auto Z-Curve Analysis"
format:
  html:
    toc: true
    embed-resources: true
execute:
  echo: true
  warning: true
  message: false
---

This report reproduces the fitted z-curve from the disclosed analysis inputs.
Keep this file in the same directory as `disclosure_table.csv` and
`zcurve_reproduction_settings.csv`, then render it with Quarto.

## Load and filter the disclosed results

The filter is the same one used for the generated analysis: an effect must be
marked as usable, have a non-empty decoded input, and have a finite z-value.
Excluded effects remain in the CSV for audit purposes.

```{r}
library(dplyr)
library(readr)
library(zcurve)

disclosure <- read_csv("disclosure_table.csv", show_col_types = FALSE)
settings <- read_csv("zcurve_reproduction_settings.csv", show_col_types = FALSE)

analysis_rows <- disclosure |>
  filter(
    usable_for_zcurve %in% TRUE,
    !is.na(analysis_input),
    nzchar(trimws(analysis_input)),
    !is.na(analysis_z),
    is.finite(analysis_z)
  )

if (nrow(analysis_rows) == 0) {
  stop("No usable finite z-curve inputs remain after filtering.")
}

analysis_rows |>
  select(source_name, analysis_input, zcurve_cluster_id, analysis_p, analysis_z)
```

## Fit the clustered z-curve

The saved seed, bootstrap count, parallel mode, worker count, clustering
method, and package version document the original fit. Using the same package
version and execution settings reproduces its bootstrap estimates.

```{r}
recorded_version <- as.character(settings$zcurve_version[[1]])
installed_version <- as.character(packageVersion("zcurve"))
if (!identical(installed_version, recorded_version)) {
  warning(
    "This analysis used zcurve ", recorded_version,
    "; the installed version is ", installed_version, "."
  )
}

zcurve_data_for_fit <- zcurve_data(
  analysis_rows$analysis_input,
  id = analysis_rows$zcurve_cluster_id
)

bootstrap_seed <- as.integer(settings$bootstrap_seed[[1]])
bootstrap_iterations <- as.integer(settings$bootstrap_iterations[[1]])
workers <- as.integer(settings$workers[[1]])
use_parallel <- isTRUE(settings$parallel[[1]]) && workers > 1L

old_workers <- zcurve.get_option("max_cores")
zcurve.options(max_cores = workers)
set.seed(bootstrap_seed)

reproduced_fit <- zcurve_clustered(
  data = zcurve_data_for_fit,
  method = as.character(settings$clustering_method[[1]]),
  bootstrap = bootstrap_iterations,
  parallel = use_parallel
)

zcurve.options(max_cores = old_workers)
summary(reproduced_fit, all = TRUE)
```

## Plot

```{r fig.width=10, fig.height=7}
plot(reproduced_fit, annotation = TRUE, CI = TRUE)
```

## Excluded effects

```{r}
disclosure |>
  filter(!is.na(zcurve_exclusion_reason), nzchar(zcurve_exclusion_reason)) |>
  select(source_name, analysis_input, analysis_p, analysis_z, zcurve_exclusion_reason)
```
